How to compute the fusion product of MV cycles in type A

### 2021-04-14 draft.tex
Updates from Overleaf

\subsection{Examples}
\rcom{I have 3 examples in mind right now: fusion product producing 1 term (maybe $1 \leftarrow 2 * 1 \rightarrow 2$), fusion product producing more than 1 term $(S_1 * S_2)$, and fusion product with multiplicities $((S_1 * S_2)^2)$}

\acom{Plus fusion product of fake MV cycles for a fourth!}

@@

Consider the subtableaux $\tau'_{i}$ of $\tau'$ and $\tau''_{i}$ of $\tau''$ where we take the boxes of $\tau'$ and $\tau''$ containing the numbers $1,\dots,i$. Let $\lambda'_{j}$ and $\lambda''_{j}$ be the corresponding sizes and $\mu'_{j}$ and $\mu'_{j}$ be the corresponding weights of the subtableaux. For each $i$, we obtain a corresponding submatrix $X_i \in \UU^{\mu'_{i}, \mu''_{i}}_{0,s}$ of $X$. These subtableaux impose rank conditions, equivalently vanishing minors, on each $X_i$ when asking them to be in $\OO^{\lambda'_{i}, \lambda''_{i}}_{0,s}$, which allows us to deduce relations on the variables in $X$. The relations must also include the new variables in the latest block and cannot have $s$ as a factor.

@@

\begin{example}
Let $G = \GL_3$ and consider the tableaux
$$\tau' = \young(12,3) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau''=\young(13,2).$$

Lusztig data: $(010)$ for $\tau'$, $(101)$ for $\tau''$

Dimensions: $(1,0,-1)$ for both.

The MV cycles corresponding to $\tau'$ and $\tau''$ are both isomorphic to $\PP^2$.
The weights are $\lambda' = \lambda'' = (2,1,0)$ and $\mu' = \mu'' = (1,1,1)$. Hence the matrix in consideration is 
\[
X = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
    0 & 1 & & & & \\
     & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 \\
     & & 0 & 1 & & \\
     & & & s & A_{23}^1 & A_{23}^2 \\
     & & & & 0 & 1 \\
     & & & & & s
\end{BMAT}
\right].
\]

For the first entry of $\mu'$ and $\mu''$, we have the following subtableaux to consider:
$$\young(1) \hspace{.5cm} \text{ and } \hspace{.5cm} \young(1).$$
Let $X_1$ be the top-left $2 \times 2$ submatrix of $X$. The subtableaux imposes the conditions $\dim \ker X_1 = 1$ and $\dim \ker (X_1-s) = 1$. We see that we do not obtain any relations from this.

For the first two entries of $\mu'$ and $\mu''$, we have the following subtableaux:
$$\young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \young(1,2).$$
Let $X_2$ be the top-left $4 \times 4$ submatrix of $X$. The left subtableau imposes the conditions $\dim \ker X_2 = 1$ and $\dim \ker X_2^2 = 2$ while the right subtableau imposes the condition that $\dim \ker (X_2 -s) = 2$. These conditions force the relation $$A_{12}^1 + sA_{12}^2 = 0.$$

The original tableaux for $X$ imposes the conditions that $\dim \ker X = 2$, $\dim \ker X^2 = 3$, $\dim \ker (X-s) = 2$, and $\dim \ker (X-s)^2 = 3$. These force the relation $$A_{23}^1 = 0.$$

Hence we consider the quotient
$$\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{23}^2,s]}{\langle A_{12}^1+sA_{12}^2,A_{23}^1,s \rangle} \cong
\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{23}^2]}{\langle A_{12}^1,A_{23}^1 \rangle}.$$
We see already that the $0$-fibre is irreducible. The tableau corresponding to the ideal $\langle A_{12}^1,A_{23}^1 \rangle$ is 
$$\young(1123,23)$$
which corresponds to the MV cycle that is the product of the MV cycles corresponding to $\tau'$ and $\tau''$.

Lusztig datum: $(111)$

Dimension: $(2,0,-2)$
\end{example}

\begin{example}
Let $G = SL_3$ and consider the tableaux
$$\tau' = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,23).$$

@@

\begin{example}
Let $G = SL_3$ and consider the following tableaux:
$$\tau' = \young(1122) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(1111,2233).$$

Lusztig data: $(200)$ for $\tau'$, $(002)$ for $\tau''$.

Dimensions: $(2,-2,0)$ for $\tau'$, $(0,2,-2)$ for $\tau''$.

The MV cycles corresponding to these tableaux are each isomorphic to $\PP^1 \times \PP^1$. 
The weights are then $\lambda' = (4,0,0)$, $\lambda'' = (4,4,0)$, $\mu' = (2,2,0)$, and $\mu'' = (4,2,2)$.
Then we are considering the following matrix:
\[
X = \left[\begin{BMAT}(e){cccccc;cccc;cc}{cccccc;cccc;cc}
    0 & 1 & & & & & & & & & & \\
     & 0 & 1 & & & & & & & & & \\
     & & 0 & 1 & & & & & & & & \\
     & & & 0 & 1 & & & & & & & \\
     & & & & 0 & 1 & & & & & & \\
     & & -s^4 & 3s^3 & -6s^2 & 4s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{12}^4 & A_{13}^1 & A_{13}^2 \\
     & & & & & & 0 & 1 & & & & \\
     & & & & & & & 0 & 1 & & & \\
     & & & & & & & & 0 & 1 & & \\
     & & & & & & & & -s^2 & 2s & A_{23}^1 & A_{23}^2 \\
     & & & & & & & & & & 0 & 1 \\
     & & & & & & & & & & -s^2 & 2s
\end{BMAT}
\right].
\]
By computer, it can be checked that we obtain the following 3 ideals:
$$
\begin{array}{cl}
    I_1 = & \langle A_{12}^1, A_{12}^2, A_{12}^3, A_{12}^4, s \rangle \\
    I_2 = & \langle A_{12}^1, A_{12}^2, A_{23}^1, A_{23}^2, s \rangle \\
    I_3 = & \langle A_{12}^1, A_{12}^2, (A_{23}^1)^2, A_{12}^4A_{23}^1 + A_{12}^3A_{23}^2, A_{12}^3A_{23}^1, (A_{12}^3)^2, s \rangle.
\end{array}
$$
It can be checked that $I_3$ has multiplicity 2 \rcom{Not sure how to make this precise and how to check it.} so the 0-fibre has 4 components, two of which are the same. The tableau corresponding to each ideal is
$$
\begin{array}{cccc}\vspace{1mm}
    \young(11111133,2222) & \text{for } I_1 & \text{Lusztig: }(202) & \dim = (2,0,-2) \\ \vspace{1mm}
    \young(11111122,2233) & \text{for } I_2 & \text{Lusztig: }(020) & \dim = (2,0,-2) \\ \vspace{1mm}
    \young(11111123,2223) & \text{for } I_3 & \text{Lusztig: }(111) & \dim = (2,0,-2).
\end{array}
$$
The MV cycle for each ideal is isomorphic to $\PP^2 \times \PP^2$.
\end{example}

\begin{example}
Let us redo example 3 but with non-dominant weights $\mu'$ and $\mu''$ such that $\mu' + \mu''$ is effective dominant. Consider the tableaux
$$\tau' = \young(22) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,33).$$
Then the weights are $\lambda' = (2,0,0)$, $\lambda'' = (2,2,0)$, $\mu' = (0,2,0)$, and $\mu'' = (2,0,2)$. Our matrix $X$ is now
\[
X = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
    0 & 1 & & & & \\
    -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 \\
     & & 0 & 1 & & \\
     & & & 0 & A_{23}^1 & A_{23}^2 \\
     & & & & 0 & 1 \\
     & & & & -s^2 & 2s
\end{BMAT}
\right].
\]
Using a computer, the ideals we now get are
$$
\begin{array}{cl}
    I_1 = & \langle A_{12}^1, A_{12}^2 \rangle \\
    I_2 = & \langle A_{23}^1, A_{23}^2 \rangle \\
    I_3 = & \langle (A_{23}^1)^2, A_{12}^2A_{23}^1 + A_{12}^1A_{23}^2, A_{12}^1A_{23}^1, (A_{12}^1)^2 \rangle. 
\end{array}
$$
The tableaux corresponding to each ideal is
$$
\begin{array}{cc}\vspace{1mm}
    \young(1133,22) & \text{for } I_1 \\ \vspace{1mm}
    \young(1122,33) & \text{for } I_2 \\ \vspace{1mm}
    \young(1123,23) & \text{for } I_3
\end{array}
$$
and the MV cycles corresponding to each are the same as before.
\end{example}

>>>>

\subsection{Examples}

% \acom{Plus fusion product of fake MV cycles for a fourth!}

@@

Consider the subtableaux $\tau'(i)$ of $\tau'$ and $\tau''(i)$ of $\tau''$ where we take the boxes of $\tau'$ and $\tau''$ containing the numbers $1,\dots,i$. Let $\lambda'(j)$ and $\lambda''(j)$ be the corresponding sizes and $\mu'(j)$ and $\mu'(j)$ be the corresponding weights of the subtableaux. For each $i$, we obtain a corresponding submatrix $X_i \in \UU^{\mu'(i), \mu''(i)}_{0,s}$ of $X$. These subtableaux impose rank conditions, equivalently vanishing minors, on each $X_i$ when asking them to be in $\OO^{\lambda'(i), \lambda''(i)}_{0,s}$, which allows us to deduce relations on the variables in $X$. The relations must also include the new variables in the latest block and cannot have $s$ as a factor.

@@

% \begin{example}
% Let $G = \GL_3$ and consider the tableaux
% $$\tau' = \young(12,3) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau''=\young(13,2).$$

% Lusztig data: $(010)$ for $\tau'$, $(101)$ for $\tau''$

% Dimensions: $(1,0,-1)$ for both.

% The MV cycles corresponding to $\tau'$ and $\tau''$ are both isomorphic to $\PP^2$.
% The weights are $\lambda' = \lambda'' = (2,1,0)$ and $\mu' = \mu'' = (1,1,1)$. Hence the matrix in consideration is 
% \[
% X = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
%     0 & 1 & & & & \\
%      & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 \\
%      & & 0 & 1 & & \\
%      & & & s & A_{23}^1 & A_{23}^2 \\
%      & & & & 0 & 1 \\
%      & & & & & s
% \end{BMAT}
% \right].
% \]

% For the first entry of $\mu'$ and $\mu''$, we have the following subtableaux to consider:
% $$\young(1) \hspace{.5cm} \text{ and } \hspace{.5cm} \young(1).$$
% Let $X_1$ be the top-left $2 \times 2$ submatrix of $X$. The subtableaux imposes the conditions $\dim \ker X_1 = 1$ and $\dim \ker (X_1-s) = 1$. We see that we do not obtain any relations from this.

% For the first two entries of $\mu'$ and $\mu''$, we have the following subtableaux:
% $$\young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \young(1,2).$$
% Let $X_2$ be the top-left $4 \times 4$ submatrix of $X$. The left subtableau imposes the conditions $\dim \ker X_2 = 1$ and $\dim \ker X_2^2 = 2$ while the right subtableau imposes the condition that $\dim \ker (X_2 -s) = 2$. These conditions force the relation $$A_{12}^1 + sA_{12}^2 = 0.$$

% The original tableaux for $X$ imposes the conditions that $\dim \ker X = 2$, $\dim \ker X^2 = 3$, $\dim \ker (X-s) = 2$, and $\dim \ker (X-s)^2 = 3$. These force the relation $$A_{23}^1 = 0.$$

% Hence we consider the quotient
% $$\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{23}^2,s]}{\langle A_{12}^1+sA_{12}^2,A_{23}^1,s \rangle} \cong
% \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{23}^2]}{\langle A_{12}^1,A_{23}^1 \rangle}.$$
% We see already that the $0$-fibre is irreducible. The tableau corresponding to the ideal $\langle A_{12}^1,A_{23}^1 \rangle$ is 
% $$\young(1123,23)$$
% which corresponds to the MV cycle that is the product of the MV cycles corresponding to $\tau'$ and $\tau''$.

% Lusztig datum: $(111)$

% Dimension: $(2,0,-2)$
% \end{example}

\begin{example}
Let $G = \GL_3$ and consider the tableaux
$$\tau' = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,23).$$

@@

% \begin{example}
% Let $G = SL_3$ and consider the following tableaux:
% $$\tau' = \young(1122) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(1111,2233).$$

% Lusztig data: $(200)$ for $\tau'$, $(002)$ for $\tau''$.

% Dimensions: $(2,-2,0)$ for $\tau'$, $(0,2,-2)$ for $\tau''$.

% The MV cycles corresponding to these tableaux are each isomorphic to $\PP^1 \times \PP^1$. 
% The weights are then $\lambda' = (4,0,0)$, $\lambda'' = (4,4,0)$, $\mu' = (2,2,0)$, and $\mu'' = (4,2,2)$.
% Then we are considering the following matrix:
% \[
% X = \left[\begin{BMAT}(e){cccccc;cccc;cc}{cccccc;cccc;cc}
%     0 & 1 & & & & & & & & & & \\
%      & 0 & 1 & & & & & & & & & \\
%      & & 0 & 1 & & & & & & & & \\
%      & & & 0 & 1 & & & & & & & \\
%      & & & & 0 & 1 & & & & & & \\
%      & & -s^4 & 3s^3 & -6s^2 & 4s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{12}^4 & A_{13}^1 & A_{13}^2 \\
%      & & & & & & 0 & 1 & & & & \\
%      & & & & & & & 0 & 1 & & & \\
%      & & & & & & & & 0 & 1 & & \\
%      & & & & & & & & -s^2 & 2s & A_{23}^1 & A_{23}^2 \\
%      & & & & & & & & & & 0 & 1 \\
%      & & & & & & & & & & -s^2 & 2s
% \end{BMAT}
% \right].
% \]
% By computer, it can be checked that we obtain the following 3 ideals:
% $$
% \begin{array}{cl}
%     I_1 = & \langle A_{12}^1, A_{12}^2, A_{12}^3, A_{12}^4, s \rangle \\
%     I_2 = & \langle A_{12}^1, A_{12}^2, A_{23}^1, A_{23}^2, s \rangle \\
%     I_3 = & \langle A_{12}^1, A_{12}^2, (A_{23}^1)^2, A_{12}^4A_{23}^1 + A_{12}^3A_{23}^2, A_{12}^3A_{23}^1, (A_{12}^3)^2, s \rangle.
% \end{array}
% $$
% It can be checked that $I_3$ has multiplicity 2 \rcom{Not sure how to make this precise and how to check it.} so the 0-fibre has 4 components, two of which are the same. The tableau corresponding to each ideal is
% $$
% \begin{array}{cccc}\vspace{1mm}
%     \young(11111133,2222) & \text{for } I_1 & \text{Lusztig: }(202) & \dim = (2,0,-2) \\ \vspace{1mm}
%     \young(11111122,2233) & \text{for } I_2 & \text{Lusztig: }(020) & \dim = (2,0,-2) \\ \vspace{1mm}
%     \young(11111123,2223) & \text{for } I_3 & \text{Lusztig: }(111) & \dim = (2,0,-2).
% \end{array}
% $$
% The MV cycle for each ideal is isomorphic to $\PP^2 \times \PP^2$.
% \end{example}

\begin{example}
Let $G = \GL_3$. Consider the tableaux
$$\tau' = \young(22) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,33).$$
Then the weights are $\lambda' = (2,0,0)$, $\lambda'' = (2,2,0)$, $\mu' = (0,2,0)$, and $\mu'' = (2,0,2)$. Our matrix $X$ is now
\[
X = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
    0 & 1 & & & & \\
    -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 \\
     & & 0 & 1 & & \\
     & & & 0 & A_{23}^1 & A_{23}^2 \\
     & & & & 0 & 1 \\
     & & & & -s^2 & 2s
\end{BMAT}
\right].
\]
Using a computer, the ideals we get are
$$
\begin{array}{cl}
    I_1 = & \langle A_{12}^1, A_{12}^2 \rangle \\
    I_2 = & \langle A_{23}^1, A_{23}^2 \rangle \\
    I_3 = & \langle (A_{23}^1)^2, A_{12}^2A_{23}^1 + A_{12}^1A_{23}^2, A_{12}^1A_{23}^1, (A_{12}^1)^2 \rangle. 
\end{array}
$$
The tableaux corresponding to each ideal is
$$
\begin{array}{cc}\vspace{1mm}
    \young(1133,22) & \text{for } I_1 \\ \vspace{1mm}
    \young(1122,33) & \text{for } I_2 \\ \vspace{1mm}
    \young(1123,23) & \text{for } I_3
\end{array}
$$
and the MV cycles corresponding to each are isomorphic to $\PP^2 \times \PP^2$.
\end{example}

Let $G = \GL_4$. There is a cluster structure on $\CC[N]$ consisting of 12 cluster variables. We list the corresponding MV cycles and tableaux:
\[\begin{array}{cccccc} \vspace{1mm}
    Z_1 &\leadsto \young(2) & Z_2 &\leadsto \young(1,3) & Z_3 &\leadsto \young(1,2,4) \\ \vspace{1mm}
    Z_{1 \leftarrow 2} &\leadsto \young(3) & Z_{1 \rightarrow 2} &\leadsto \young(2,3) & Z_{2 \leftarrow 3} &\leadsto \young(1,4) \\ \vspace{1mm}
     Z_{2 \rightarrow 3} &\leadsto \young(1,3,4) & Z_{in} &\leadsto \young(2,4) & Z_{out} &\leadsto \young(13,2,4)  \\
    Z_{P_1} &\leadsto \young(2,3,4) & Z_{P_2} &\leadsto \young(3,4) & Z_{P_3} &\leadsto \young(4)
\end{array}\]

We show that the cluster relations in $\CC[N]$ are also true for the fusion product of the corresponding MV cycles.

For each of the 15 exchange relations, we state the associated matrix $X$, the relations acquired from each submatrix $X_i$, the ideal generated by said relations, and the corresponding tableaux from the ideal.

\begin{example}
Consider the product $Z_1 * Z_2$, so the tableaux are
\[
\young(2) \text{ and } \young(1,3).
\]
Our matrix is
\[
X = \left[\begin{BMAT}(e){c;c;c}{c;c;c}
    s & A_{12}^1 & A_{13}^1 \\
     & 0 & A_{23}^1 \\
     & & s
\end{BMAT}
\right].
\]
The relations from the submatrices are:
\[
\begin{array}{c|c}
    \text{Submatrix} & \text{Relations} \\ \hline
    X_3 & A_{12}^1A_{23}^1+sA_{13}^1
\end{array}.
\]
Hence our ideal is
$$\langle A_{12}^1A_{23}^1+sA_{13}^1,s \rangle = 
\langle A_{12}^1,s \rangle \cap \langle A_{23}^1,s \rangle.$$
The tableau for each ideal is
\[\begin{array}{cccc}\vspace{1mm}
    \langle A_{12}^1,s \rangle &\leadsto \young(13,2) &\equiv \young(3) &\leadsto Z_{Z_{1 \leftarrow 2}} \\ 
    \langle A_{23}^1,s \rangle &\leadsto \young(12,3) &\equiv \young(2,3) &\leadsto Z_{Z_{1 \rightarrow 2}}
\end{array}
\]
so $Z_1 * Z_2 = Z_{1 \leftarrow 2} + Z_{1 \rightarrow 2}$.
\end{example}

\begin{example}
Consider the product $Z_2 * Z_3$, so the tableaux are 
\[
\young(1,3) \text{ and } \young(1,2,4).
\]
Our matrix is 
\[
X = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
    0 & 1 & & & \\
     & s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
     & & s & A_{23}^1 & A_{24}^1 \\
     & & & 0 & A_{34}^1 \\
     & & & & s
\end{BMAT}
\right].
\]
The relations from the submatrices are:
\[
\begin{array}{c|c}
    \text{Submatrix} & \text{Relations} \\ \hline
    X_2 & A_{12}^1 \\
    X_3 & A_{13}^1 \\
    X_4 & A_{14}^1, A_{23}^1A_{34}^1 + sA_{24}^1
\end{array}.
\]
Hence our ideal decomposes into 
\[
\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{14}^1,s \rangle \cap \langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle.
\]
The tableau for each ideal is
\[\begin{array}{cccc}\vspace{1mm}
    \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{14}^1,s \rangle &\leadsto \young(11,24,3) &\equiv \young(1,4) &\leadsto Z_{2 \leftarrow 3} \\ 
    \langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle &\leadsto \young(11,23,4) &\equiv \young(1,3,4) &\leadsto Z_{2 \rightarrow 3}
\end{array}
\]
so $Z_2 * Z_3 = Z_{2 \leftarrow 3} + Z_{2 \rightarrow 3}$.
\end{example}

\begin{example}
Consider the product $Z_1 * Z_{2 \rightarrow 3}$, so the tableaux are 
\[
\young(2) \text{ and } \young(1,3,4).
\]
Our matrix is 
\[
X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
    s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
     & 0 & A_{23}^1 & A_{24}^1 \\
     & & s & A_{34}^1 \\
     & & & s
\end{BMAT}
\right].
\]
The relations from the submatrices are:
\[
\begin{array}{c|c}
    \text{Submatrix} & \text{Relations} \\ \hline
    X_3 & A_{12}^1A_{23}^1 + sA_{13}^1 \\
    X_4 & A_{34}^1, A_{12}^1A_{24}^1 + sA_{14}^1, A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1
\end{array}.
\]
Hence our ideal decomposes into 
\[
\langle A_{23}^1,A_{24}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{34}^1,A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1,s \rangle.
\]
The tableau for each ideal is
\[\begin{array}{cccc}\vspace{1mm}
    \langle A_{23}^1,A_{24}^1,A_{34}^1,s \rangle &\leadsto \young(12,3,4) &\equiv \young(2,3,4) &\leadsto Z_{P_1} \\ 
    \langle A_{12}^1,A_{34}^1,A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1,s \rangle &\leadsto \young(13,2,4) & &\leadsto Z_{out}
\end{array}
\]
so $Z_1 * Z_{2 \rightarrow 3} = Z_{P_1} + Z_{out}$.
\end{example}

\begin{example}
Consider the product $Z_1 * Z_{2 \leftarrow 3}$, so the tableaux are 
\[
\young(2) \text{ and } \young(1,4).
\]
As the sum of the weights is not dominant, we will instead be using the tableaux
\[
\young(2) \text{ and } \young(11,24,3).
\]
Our matrix is 
\[
X = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
    0 & 1 & & & & \\
    -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
     & & 0 & 1 & & \\
     & & & s & A_{23}^1 & A_{24}^1 \\
     & & & & s & A_{34}^1 \\
     & & & & & s
\end{BMAT}
\right].
\]
The relations from the submatrices are:
\[
\begin{array}{c|c}
    \text{Submatrix} & \text{Relations} \\ \hline
    X_2 & A_{12}^1 + sA_{12}^2 \\
    X_3 & A_{13}^1, A_{23}^1 \\
    X_4 & A_{12}^2A_{24}^1 + sA_{14}^1, A_{12}^1A_{24}^1 - s^2A_{14}^1 
\end{array}.
\]
Hence our ideal decomposes into 
\[
\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s \rangle \cap \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle.
\]
The tableau for each ideal is
\[\begin{array}{cccc}\vspace{1mm}
    \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s \rangle &\leadsto \young(114,22,3) &\equiv \young(4) &\leadsto Z_{P_3} \\ 
    \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle &\leadsto \young(112,24,3) &\equiv \young(2,4) &\leadsto Z_{in}
\end{array}
\]
so $Z_1 * Z_{2 \leftarrow 3} = Z_{P_3} + Z_{in}$.
\end{example}

\begin{example}
Consider the product $Z_3 * Z_{1 \rightarrow 2}$, so the tableaux are 
\[
\young(1,2,4) \text{ and } \young(2,3).
\]
As the sum of the weights is not dominant, we will instead be using the tableaux
\[
\young(1,2,4) \text{ and } \young(12,3).
\]
Our matrix is 
\[
X = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
    0 & 1 & & & & \\
     & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
     & & 0 & 1 & & \\
     & & & s & A_{23}^1 & A_{24}^1 \\
     & & & & s & A_{34}^1 \\
     & & & & & 0
\end{BMAT}
\right].
\]
The relations from the submatrices are:
\[
\begin{array}{c|c}
    \text{Submatrix} & \text{Relations} \\ \hline
    X_2 & A_{12}^1 \\
    X_3 & A_{23}^1 \\
    X_4 & A_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1 
\end{array}.
\]
Hence our ideal decomposes into 
\[
\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle \cap \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle.
\]
The tableau for each ideal is
\[\begin{array}{cccc}\vspace{1mm}
    \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle &\leadsto \young(112,24,3) &\equiv \young(1,4) &\leadsto Z_{in} \\ 
    \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle &\leadsto \young(112,23,4) &\equiv \young(1,3,4) &\leadsto Z_{P_1}
\end{array}
\]
so $Z_3 * Z_{1 \rightarrow 2} = Z_{in} + Z_{P_1}$.
\end{example}

\begin{example}
Consider the product $Z_3 * Z_{1 \leftarrow 2}$, so the tableaux are 
\[
\young(1,2,4) \text{ and } \young(3).
\]
Our matrix is 
\[
X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
    0 & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
     & 0 & A_{23}^1 & A_{24}^1 \\
     & & s & A_{34}^1 \\
     & & & 0
\end{BMAT}
\right].
\]
The relations from the submatrices are:
\[
\begin{array}{c|c}
    \text{Submatrix} & \text{Relations} \\ \hline
    X_2 & A_{12}^1 \\
    X_4 & A_{23}^1A_{34}^1 - sA_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
\end{array}.
\]
Hence our ideal decomposes into 
\[
\langle A_{12}^1,A_{13}^1,A_{23}^1,s \rangle \cap \langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1,s \rangle.
\]
The tableau for each ideal is
\[\begin{array}{cccc}\vspace{1mm}
    \langle A_{12}^1,A_{13}^1,A_{23}^1,s \rangle &\leadsto \young(14,2,3) &\equiv \young(4) &\leadsto Z_{P_3} \\ 
    \langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1,s \rangle &\leadsto \young(13,2,4) & &\leadsto Z_{out}
\end{array}
\]
so $Z_3 * Z_{1 \leftarrow 2} = Z_{P_3} + Z_{out}$.
\end{example}

\begin{example}
Consider the product $Z_{1 \leftarrow 2} * Z_{2 \leftarrow 3}$, so the tableaux are 
\[
\young(3) \text{ and } \young(1,4).
\]
As the sum of the weights is not dominant, we will instead be using the tableaux
\[
\young(13,2) \text{ and } \young(1,4).
\]
Our matrix is 
\[
X = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
    0 & 1 & & & \\
     & s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
     & & 0 & A_{23}^1 & A_{24}^1 \\
     & & & 0 & A_{34}^1 \\
     & & & & s
\end{BMAT}
\right].
\]
The relations from the submatrices are:
\[
\begin{array}{c|c}
    \text{Submatrix} & \text{Relations} \\ \hline
    X_2 & A_{12}^1 \\
    X_4 & A_{13}^1A_{34}^1 + sA_{14}^1
\end{array}.
\]
Hence our ideal is 
\[
\langle A_{12}^1,A_{13}^1A_{34}^1+sA_{14}^1,s \rangle
= \langle A_{12}^1,A_{13}^1,s \rangle \cap \langle A_{12}^1,A_{34}^1,s \rangle.
\]
The tableau for each ideal is
\[\begin{array}{cccc}\vspace{1mm}
    \langle A_{12}^1,A_{13}^1,s \rangle &\leadsto \young(114,23) &\equiv \young(14,3) &\leadsto Z_2 Z_{P_3} \\ 
    \langle A_{12}^1,A_{34}^1,s \rangle &\leadsto \young(113,24) &\equiv \young(3,4) &\leadsto Z_{P_2}
\end{array}
\]
so $Z_{1 \leftarrow 2} * Z_{2 \leftarrow 3} = Z_2 Z_{P_3} + Z_{P_2}$.
\end{example}

\begin{example}
Consider the product $Z_{1 \rightarrow 2} * Z_{2 \rightarrow 3}$, so the tableaux are 
\[
\young(2,3) \text{ and } \young(1,3,4).
\]
As the sum of the weights is not dominant, we will instead be using the tableaux
\[
\young(12,23) \text{ and } \young(1,3,4).
\]
Our matrix is 
\[
X = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
    0 & 1 & & & & & \\
     & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 \\
     & & 0 & 1 & & & \\
     & & & 0 & A_{23}^1 & A_{23}^2 & A_{24}^1 \\
     & & & & 0 & 1 & \\
     & & & & & s & A_{34}^1 \\
     & & & & & & s
\end{BMAT}
\right].
\]
The relations from the submatrices are:
\[
\begin{array}{c|c}
    \text{Submatrix} & \text{Relations} \\ \hline
    X_2 & A_{12}^1 \\
    X_3 & A_{23}^1, A_{12}^2A_{23}^2 + A_{13}^1 + sA_{13}^2 \\
    X_4 & A_{34}^1, A_{12}^2A_{24}^1 + sA_{14}^1, sA_{23}^2A_{14}^1 - sA_{13}^2A_{24}^1 - A_{13}^1A_{24}^1
\end{array}.
\]
Hence our ideal decomposes into 
\[
\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,A_{12}^2A_{23}^2+A_{13}^1,s \rangle.
\]
The tableau for each ideal is
\[\begin{array}{cccc}\vspace{1mm}
    \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle &\leadsto \young(113,224,3) &\equiv \young(3,4) &\leadsto Z_{P_2} \\ 
    \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,A_{12}^2A_{23}^2+A_{13}^1,s \rangle &\leadsto \young(112,233,4) &\equiv \young(12,33,4) &\leadsto Z_2 Z_{P_1}
\end{array}
\]
so $Z_{1 \rightarrow 2} * Z_{2 \rightarrow 3} = Z_{P_2} + Z_2 Z_{P_1}$.
\end{example}
